---
title: "Aesthetic Theme"
subtitle: "for Quarto revealjs"
author: "Akiru Kato"
format: aesthetic-revealjs
---

# AESTHETIC

:::{.aesthetic-windows-95-container-indent}
[AESTHETIC](https://torch2424.github.io/aesthetic-css/) is a vaporwave CSS framework written by Aaron Turner and Daniel Gomez.

[This is a Quarto reveal.js theme that is based on AESTHETIC.]{.aesthetic-pepsi-cola-color}
:::

## Header 2

### Header 3

:::{.aesthetic-windows-95-container-indent}
Normal text inside a `.aethetic-windows-95-container-indent`

**Bold text**

*italics*

~~strikethrough~~

[links](https://www.xaringan.gallery/).
:::

## Ordered list

1.  First item
2.  Second item
3.  Third item
    1.  Indented item
    2.  Indented item
4.  Fourth item

## Unordered list

-   First item
-   Second item
-   Third item
-   Fourth item

## Table

| Column 1 | Column 2 | Column 3 |
|----------|----------|----------|
| 1        | 2        | 3        |
| 4        | 5        | 6        |

## Block quotes

> Dorothy followed her through many of the beautiful rooms in her castle.

:::{.aesthetic-effect-crt}
> This is a block quotes with CRT effect.
:::

## Equations

inline math: $E = mc^{2}$

display math:

$$E = mc^{2}$$

## Code expressions

Code chunks and output

```{r}
#| echo: true
lm(mpg ~ disp, data = mtcars)
```

## ggplot2

```{r scatter}
#| echo: true
#| warning: false
#| output-location: slide
library(ggplot2)

colors <- c("#76c442", "#f2c409", "#ce372b")

ggplot(modeldata::penguins) +
  aes(bill_length_mm, bill_depth_mm,
      color = species) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = colors)
```

## Tabsets

:::{.panel-tabset}

### Tab A

Content for `Tab A`

### Tab B

Content for `Tab B`

:::

## Raw contents

### Text glitch

```{=html}
<div>
  <h4 class="aesthetic-25-transparent-color aesthetic-effect-text-glitch" data-glitch="A E S T H E T I C">A E S T H E T I C</h4>
</div>
```

### Loaders

```{=html}
<div class="aesthetic-windows-95-modal">

  <!-- Title Bar -->
  <div class="aesthetic-windows-95-modal-title-bar">

    <div class="aesthetic-windows-95-modal-title-bar-text">
      AESTHETIC
    </div>

    <div class="aesthetic-windows-95-modal-title-bar-controls">
      <div class="aesthetic-windows-95-button-title-bar">
        <button>
          X
        </button>
      </div>
    </div>

  </div>

  <!-- Content -->
  <!-- Could be a tabbed container, or a set of dropdowns, etc... -->
  <div class="aesthetic-windows-95-modal-content">
    <h4>Windows 95 Boot Loader</h4>
    <div class="aesthetic-windows-95-boot-loader">
      <div></div>
    </div>

    <h4>Windows 95 Loader</h4>
    <div class="aesthetic-windows-95-loader">
      <div></div>
      <div></div>
      <div></div>
    </div>

    <h4>Windows XP Loader</h4>
    <div class="aesthetic-windows-xp-loader">
      <div></div>
      <div></div>
      <div></div>
    </div>
  </div>
</div>
```

## Fonts

:::{.aesthetic-windows-95-container-indent}
:::{.aesthetic-font-modifier-outline-black}
Black outline text
:::

:::{.aesthetic-font-modifier-outline-pink}
Pink outline text
:::

:::{.aesthetic-font-modifier-outline-purple}
Purple outline text
:::
:::

## Colors

:::{.aesthetic-white-bg-color}
:::{.aesthetic-pepsi-red-color}
Pepsi red color text inside white background
:::
:::

:::{.aesthetic-arizona-pink-bg-color}
Arizona pink
:::

:::{.aesthetic-arizona-lime-bg-color}
Arizona lime
:::

:::{.aesthetic-arizona-green-bg-color}
Arizona green
:::

:::{.aesthetic-arizona-blue-bg-color}
Arizona blue
:::

## 日本語のテキスト

### 見出し3

:::{.aesthetic-windows-95-container-indent}
あのイーハトーヴォの透きとおった風

**あのイーハトーヴォの透きとおった風
**

*あのイーハトーヴォの透きとおった風*

~~あのイーハトーヴォの透きとおった風~~

:::
